### 2014-05-16 ApTranscriptome_TR.Rmd

```{r gsea_by_type_table, echo = FALSE, results = 'asis'}
pandoc.table(Ap.gsea1[, 1:3], caption = "Enriched GO terms for each thermal-response category")
#print(xtable(Ap.gsea1[ , 1:3], comment = getOption("xtable.comment", FALSE)))
```

@@

```{r gsea_setdiff_table, echo = FALSE, results = 'asis'}
pandoc.table(Ap.setdiff.gsea[ , 1:4], caption = "Enriched GO terms found in one species but not the other for each thermal-response category")
#print(xtable(Ap.setdiff.gsea[ , 1:4], comment = getOption("xtable.comment", FALSE)))
```

>>>>

```{r gsea_by_type_table, echo = FALSE, results = 'asis'}
#pandoc.table(Ap.gsea1[, 1:3], caption = "Enriched GO terms for each thermal-response category")
print(xtable(Ap.gsea1[ , 1:3], comment = getOption("xtable.comment", FALSE)))
```

@@

```{r gsea_setdiff_table, echo = FALSE, results = 'asis'}
#pandoc.table(Ap.setdiff.gsea[ , 1:4], caption = "Enriched GO terms found in one species but not the other for each thermal-response category")
print(xtable(Ap.setdiff.gsea[ , 1:4], comment = getOption("xtable.comment", FALSE)))
```
